Fitting metabolic models to dissolved oxygen data: The Estuarine BAyesian Single-station Estimation method

### 2023-08-27 manu-draft.qmd
reworking some figures, optex now has options for ylim

![Summaries of median Nash-Sutcliffe Efficiency (NSE) values across all parameters for the comparisons of EBASE and synthetic model outputs separated by different combinations of prior values. Summaries are shown relative to the difference from the grand median across all comparisons. Each result on the x-axis represents the median values for which the combination prior applies, e.g., all results from @fig-priorcomp where $\mu$ is high or low for the $a$ parameter using a one day optimization period. Point size represents the inter-quartile range of median NSE values for each result.](figs/priorsumcomp.png){#fig-priorsumcomp}

@@

![Comparison of EBASE results for the best and worst performing models to a synthetic time series created with known metabolic parameters. The best and worst performing models for the one day (a, b), seven day (c, d), and thirty day (e, f) optimization periods are based on the EBASE results with prior distributions that produced the highest and lowest median Nash-Sutcliffe Efficenciy values across all parameter estimates (@fig-priorcomp). The results are averaged at the time step of the model optimization period. The $b$ parameter is fixed at 0.251 $\left(\text{cm}/\text{hr}\right)/\left(\text{m}^2/\text{s}^2\right)$.](figs/optex.png){#fig-optex fig-align="center"}

>>>>

![Summaries of % change in Nash-Sutcliffe Efficiency (NSE) values across all the comparisons of EBASE and the five synthetic model outputs separated by different combinations of prior values. Summaries are shown relative to the change from the median for each comparison group (i.e., optimization period and prior parameter, $n$ = 32). Each result on the x-axis represents the median values for which the combination prior applies. For example, the points in the upper left panel that are fartheset to the left summarize the results from @fig-priorcomp where $\mu$ is high or low for the $a$ parameter using a one day optimization period. Point size represents the inter-quartile range of median NSE values for each result ($n$ = 8) .](figs/priorsumcomp.png){#fig-priorsumcomp}

@@

![Comparison of EBASE results for the best and worst performing models to a synthetic time series created with known metabolic parameters. The best and worst performing models for the one day (a, b), seven day (c, d), and thirty day (e, f) optimization periods are based on the EBASE results with prior distributions that produced the highest and lowest median Nash-Sutcliffe Efficency values across all parameter estimates (@fig-priorcomp). The results are averaged at the time step of the model optimization period. The $b$ parameter is fixed at 0.251 $\left(\text{cm}/\text{hr}\right)/\left(\text{m}^2/\text{s}^2\right)$.](figs/optex.png){#fig-optex fig-align="center"}
